Reflections from reproductions

### 2024-10-16 pages/reflections.qmd
docs(reflections): add hernandez 2015

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | 🟡 | ✅ | ✅ | <!--TODO--> | <!--TODO--> | ❌ |

@@

@hernandez_optimal_2015: <!--TODO-->

@@

* The `import` statements can be sufficient in indicating all the packages required but this is not always the case if there are "hidden"/unmentioned dependencies that don't get imported
* There are various options for listing the packages (e.g. comprehensive import statements, installation lines in the script, environment files).
* This was a common issue.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | 🟡 | 🟡 | 🟡 | <!--TODO--> | <!--TODO--> | 🟡 |

@@

@hernandez_optimal_2015: <!--TODO-->

@@

* Models will sometimes work with the latest versions of packages, but likewise, you will sometimes need to backdate as it no longer works with the latest
* For Python, it was very easy to "backdate" the python and package versions. However, I found this very difficult to in R, and ended up always using the latest versions.
* Versions are sometimes provided elsewhere (e.g. in paper, in other repositories), but would be handy to be in model repository itself
* This was a very common issue.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ✅ | ❌ | ✅ | ✅ | ✅ | <!--TODO--> | <!--TODO--> | ✅ |

@@

@hernandez_optimal_2015: <!--TODO-->

@@

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ✅ | ✅ | ✅ | ✅ | <!--TODO--> | <!--TODO--> | ✅ |

@shoaib_simulation_2021: Not met. The model is set up as classes and run using a function. However, it is not designed to allow any variation in inputs. Everything uses default inputs, and it designed in such a way that - if you wish to vary model parameters - you need to directly change these in the script itself. This meant you couldn't run multiple versions of the model using the same script. It also meant hidden errors were more likely (e.g. if miss changing a parameter somewhere, or input the wrong parameters and don’t realise).

@@

@hernandez_optimal_2015: <!--TODO-->

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | 🟡 | ❌ | ✅ | N/A | <!--TODO--> | <!--TODO--> | ✅ |

@@

@hernandez_optimal_2015: <!--TODO-->

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | ✅ |

@@

@hernandez_optimal_2015: <!--TODO-->

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ✅ | ✅ | ❌ | ✅ | <!--TODO--> | <!--TODO--> | ✅ |

@@

@hernandez_optimal_2015: <!--TODO-->

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ✅ | 🟡 | 🟡 | <!--TODO--> | <!--TODO--> | ❌ |

@@

@hernandez_optimal_2015: <!--TODO-->

@@

## Run time, memory usage and file size

@@

* @shoaib_simulation_2021: Add parallel processing and ran fewer replications
* @huang_optimizing_2019: No changes made.
* @lim_staff_2020: Add parallel processing
* @kim_modelling_2021: Reduced number of people in simulation, and switched from serial to the provided parallel option.
* @anagnostou_facs-charm_2022: Model was super quick which made it really easy to run and re-run each time
* @johnson_cost_2021: <!--TODO-->
* @hernandez_optimal_2015: <!--TODO-->
* @wood_value_2021: No changes made, but unlike other reproduction, didn't try to run at smaller amounts - just set it to run as-is over the weekend.

@@

* @shoaib_simulation_2021: <!--TODO-->
* @huang_optimizing_2019: <!--TODO-->
* @lim_staff_2020: <!--TODO-->
* @kim_modelling_2021: <!--TODO-->
* @anagnostou_facs-charm_2022: <!--TODO-->
* @johnson_cost_2021: <!--TODO-->
* @hernandez_optimal_2015: <!--TODO-->
* @wood_value_2021: Aggregate results files are small (327 kB), but raw results files are very large (2.38 GiB), and even when compressed to `.csv.gz` (128 MiB) require using of GitHub LFS

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| 🟡 | ❌ | ❌ | ❌ | N/A | <!--TODO--> | <!--TODO--> | 🟡 |

@shoaib_simulation_2021: Partially met. Run time stated in paper but not repository.

@@

@kim_modelling_2021: Not met. A prior paper describing the model development mentions the run time, but not the current paper or repository.

@@

@hernandez_optimal_2015: <!--TODO-->

@@

* For long models with no statement, it can take a while to realise that it's not an error in the code or anything, but actually just a long run time! And hard to know how long to expect, and whether it is without the capacities of your machine and so on.
* Common issue.

@@

@hernandez_optimal_2015: <!--TODO-->

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ❌ | N/A | <!--TODO--> | <!--TODO--> | ✅ |

@@

@hernandez_optimal_2015: <!--TODO-->

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ❌ | ✅ | <!--TODO--> | <!--TODO--> | ✅ |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| 🟡 | ❌ | 🟡 | ✅ | ✅ | <!--TODO--> | <!--TODO--> | ✅ |

@@

@hernandez_optimal_2015: <!--TODO-->

@@

* At least provide a script that can run the baseline model as in the paper (even if not providing the scenarios)
* This can introduce difficulties - when some parameters are wrong, you rely on the paper to check which parameters are correct or not, but if the paper doesn't mention every single parameter (which is reasonably likely, as this includes those not varied by scenarios), then you aren't able to be sure that the model you are running is correct.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ✅ | ✅ | <!--TODO--> | <!--TODO--> | ✅ |

@@

@hernandez_optimal_2015: <!--TODO-->

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | 🟡 | N/A | N/A | <!--TODO--> | <!--TODO--> | N/A |

@@

@hernandez_optimal_2015: <!--TODO-->

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ✅ | N/A | N/A | N/A | <!--TODO--> | <!--TODO--> | N/A |

@@

@hernandez_optimal_2015: <!--TODO-->

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ✅ | ❌ | ❌ | ❌ | ✅ | <!--TODO--> | <!--TODO--> | ✅ |

@@

@hernandez_optimal_2015: <!--TODO-->

@wood_value_2021: Outputs to `.csv` files.

@@

@hernandez_optimal_2015: <!--TODO-->

@@

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ✅ | ✅ | <!--TODO--> | <!--TODO--> | ✅ |

@@

@hernandez_optimal_2015: <!--TODO-->

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | N/A | 🟡 | ❌ | N/A | <!--TODO--> | <!--TODO--> | ✅ |

@@

@hernandez_optimal_2015: <!--TODO-->

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ❌ | ❌ | <!--TODO--> | <!--TODO--> | ✅ |

@@

@hernandez_optimal_2015: <!--TODO-->

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | N/A | ❌ | N/A | <!--TODO--> | <!--TODO--> | N/A |

@@

@lim_staff_2020, @anagnostou_facs-charm_2022, @wood_value_2021: Not applicable (no in-text results).

@hernandez_optimal_2015: <!--TODO-->

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | 🟡 | ✅ | <!--TODO--> | <!--TODO--> | ❌ |

@@

Include tick marks/grid lines on figures, so it is easier to read across and judge whether a result is above or below a certain Y value.

@anagnostou_facs-charm_2022: Included data dictionary for input parameters. Although I didn’t need this, this would have been great if I needed to change the input parameters at all.

@@

* Include grid lines
* Include data dictionaries

>>>>

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | 🟡 | ✅ | ✅ | <!--TODO--> | 🟡 | ❌ |

@@

@hernandez_optimal_2015: Partially met. Some (but not all) of the required packages were listed in the paper.

@@

* The `import` statements can be sufficient in indicating all the packages required but this is not always the case if there are "hidden"/unmentioned dependencies that don't get imported
* There are various options for listing the packages (e.g. comprehensive import statements, installation lines in the script, environment files).
* Ideally mention this in repository, not just the paper.
* This was a common issue.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | 🟡 | 🟡 | 🟡 | <!--TODO--> | 🟡 | 🟡 |

@@

@hernandez_optimal_2015: Partially. Versions of Python, R and some (but not all) packages given in the paper. Some versions weren't very specific (e.g. Python 2.7 v.s. something specific like 2.7.12)

@@

* Models will sometimes work with the latest versions of packages, but likewise, you will sometimes need to backdate as it no longer works with the latest
* For Python, it was very easy to "backdate" the python and package versions. However, I found this very difficult to in R, and ended up always using the latest versions.
* Versions are sometimes provided elsewhere (e.g. in paper, in other repositories), but would be handy to be in model repository itself.
* Handy to provide specific versions too, particularly when there can be reasonably large changes between minor versions.
* This was a very common issue.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ✅ | ❌ | ✅ | ✅ | ✅ | <!--TODO--> | ✅ | ✅ |

@@

@hernandez_optimal_2015: Fully met. The model (python code) can be run from `main.py`.

@@

<!--TODO: Consider overlap between some of these and how clear it is. I seperated to seperate out the script structure v.s. hard coding v.s. providing parameters and scenarios later. Consider whether evaluation for Shoaib below feels correct or not. -->

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ✅ | ✅ | ✅ | ✅ | <!--TODO--> | ✅ | ✅ |

@shoaib_simulation_2021: Not met. The model is set up as classes and run using a function. However, it is not designed to allow any variation in inputs. Everything uses default inputs, and it designed in such a way that - if you wish to vary model parameters - you need to directly change these in the script itself.

@@

@hernandez_optimal_2015: Fully met. Model created from classes, which accept some inputs and can run the model.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | 🟡 | ❌ | ✅ | N/A | <!--TODO--> | 🟡 | ✅ |

@@

@hernandez_optimal_2015: Partially met. Did not hard code, runs, population, generations, and percent pre-screened. However, did hard code other parameters like bi-objective v.s tri-objective model and bounding. Also, it was pretty tricky to change percent pre-screened, as it assumed you provided a `.txt` file for each %.

@@

<!--TODO: Consider whether this is something to keep? Did any have an issue with relative file paths? Or was it more that I saw an issue with relative file paths that were tricky to change? Have mentioned this is a bit under "Saves output to a file"-->

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | ✅ | ✅ |

@@

@hernandez_optimal_2015: Fully met. Creates folder in current working directory based on date/time to store results.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ✅ | ✅ | ❌ | ✅ | <!--TODO--> | ✅ | ✅ |

@@

@hernandez_optimal_2015: Fully met.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ✅ | 🟡 | 🟡 | <!--TODO--> | 🟡 | ❌ |

@@

@hernandez_optimal_2015: Partially met. There are some comments and doc-strings, but not comprehensively.

@@

## Run time and memory usage

@@

* @shoaib_simulation_2021: Add parallel processing and ran fewer replications
* @huang_optimizing_2019: No changes made.
* @lim_staff_2020: Add parallel processing
* @kim_modelling_2021: Reduced number of people in simulation, and switched from serial to the provided parallel option.
* @anagnostou_facs-charm_2022: Model was super quick which made it really easy to run and re-run each time
* @johnson_cost_2021: <!--TODO-->
* @hernandez_optimal_2015: Add parallel processing, did not run one of the scenarios (it was very long, and hadn't managed to reproduce other parts of same figure regardless), and experimented with reducing parameters for evolutionary algorithm (but, in the end, ran with full parameters, though lower were helpful while working through and troubleshooting).
* @wood_value_2021: No changes made, but unlike other reproduction, didn't try to run at smaller amounts - just set it to run as-is over the weekend.

@@

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ✅ | ❌ | ❌ | ❌ | N/A | <!--TODO--> | 🟡 | 🟡 |

@shoaib_simulation_2021: Fully met. Run time stated in paper (but not repository).

@@

@kim_modelling_2021: Not met. A prior paper describing the model development mentions the run time, but not the current paper or repository, so this is easily missed.

@@

@hernandez_optimal_2015: Partially met. Some of the run times are mentioned in the paper, but not all, although this did help indicate that we would anticipate other s scenarios to similarly take hours to run.

@@

* For long models with no statement, it can take a while to realise that it's not an error in the code or anything, but actually just a long run time! And hard to know how long to expect, and whether it is without the capacities of your machine and so on.
* Ideally include statement of run time in repository as well as paper.
* Ideally include run time of all components of analysis (e.g. all scenarios).
* Common issue.

@@

@hernandez_optimal_2015: <!--TODO: This had long run times but I don't know if it was computationally expensive or not. May need to run again for a while and see what memory usage is-->

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ❌ | N/A | <!--TODO--> | ❌ | ✅ |

@@

@hernandez_optimal_2015: Not met. Took a while to figure out how to implement scenarios.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ❌ | ✅ | <!--TODO--> | ✅ | ✅ |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| 🟡 | ❌ | 🟡 | ✅ | ✅ | <!--TODO--> | ❌ | ✅ |

@@

@hernandez_optimal_2015: Not met. As agreed with the author, this is likely the primary reason for the discrepancy in these results - they are very close, and we see similar patterns, but not reproduced. Unfortunately, several parameters were wrong, and although we changed those we spotted, we anticipate there could be others we hadn't spotted that might explain the remaining discrepancies.

@@

* At least provide a script that can run the baseline model as in the paper (even if not providing the scenarios)
* This can introduce difficulties - when some parameters are wrong, you rely on the paper to check which parameters are correct or not, but if the paper doesn't mention every single parameter (which is reasonably likely, as this includes those not varied by scenarios), then you aren't able to be sure that the model you are running is correct.
* This can make a really big difference, and be likely cause of managing to reproduce everything v.s. nothing, if it impacts all aspects of the results.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ✅ | ✅ | <!--TODO--> | ❌ | ✅ |

@@

@hernandez_optimal_2015: Not met. The results have a large impact by the bounding set, but this was not mentioned in the paper or repository, and required me looking at the numbers in results and GitHub commit history to estimate the appropriate bounds to use.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | 🟡 | N/A | N/A | <!--TODO--> | 🟡 | N/A |

@@

@hernandez_optimal_2015: Most parameters are relatively easily identified from the text or figure legends (though would be easier if provided in a table or similar). Parameter for bounding was not provided in paper.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ✅ | N/A | N/A | N/A | <!--TODO--> | N/A | N/A |

@@

@hernandez_optimal_2015: Not applicable.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ✅ | ❌ | ❌ | ❌ | ✅ | <!--TODO--> | ✅ | ✅ |

@@

@hernandez_optimal_2015: Fully met. Outputs to `.txt` files.

@wood_value_2021: Fully met. Outputs to `.csv` files.

@@

@hernandez_optimal_2015: Fully met. Straightforward with key information provided.

@@

* @shoaib_simulation_2021: Not relevant (results files **<35 kB**)
* @huang_optimizing_2019: Provided code didn't save results to file. When I saved to file, these were large, so I compressed to `.csv.gz`, which made them small enough that GitHub was still happy (**26 MB**).
* @lim_staff_2020: Provided code didn't save results to file. When I saved to file, these were small, so not relevant (results files **<60 kB**)
* @kim_modelling_2021: Provided code didn't save results to file. When I saved to file, these were small, so not relevant (results files **<1 kB**)
* @anagnostou_facs-charm_2022: Not relevant (results file **34 kB**)
* @johnson_cost_2021: <!--TODO-->
* @hernandez_optimal_2015: Not relevant (aggregate results files **<10 kB**).
* @wood_value_2021: Aggregate results files are small (**327 kB**), but raw results files are very large (**2.38 GB**), and even when compressed to `.csv.gz` (**128 MB**) require using of GitHub LFS

**Reflections:** <!--TODO: Update reflections once add Johnson -->

* For most studies, this was not relevant, with outputs relatively small
* I only really found this to be an issue when files exceeded GitHub threshold. [GitHub](https://docs.github.com/en/repositories/working-with-files/managing-large-files/about-large-files-on-github) give warning over 50 MB, blocks files over 100 MB, requiring you to use GitHub LFS. Recommends repositories ideally <1 GB and for sure < 5GB. [GitHub LFS](https://docs.github.com/en/repositories/working-with-files/managing-large-files/about-storage-and-bandwidth-usage) has limits on storage and bandwith use (1GB of each).

## Do not output excessive numbers of files

I have not evaluated like as a criteria, as a large number of files is not inherently a bad thing, and might be difficult to avoid.

Regarding number of files:

* @shoaib_simulation_2021: Not relevant.
* @huang_optimizing_2019: Not relevant.
* @lim_staff_2020: Not relevant.
* @kim_modelling_2021: Not relevant.
* @anagnostou_facs-charm_2022: Not relevant.
* @johnson_cost_2021: <!--TODO-->
* @hernandez_optimal_2015: The default behaviour of the script was to output **lots of files** from each round (so you could easily have 90, 100, 200+ files), which were then **not** used in analysis (as it just depended on an aggregate results file). Although these individual files might be useful during quality control, as a default behaviour of the script, it could easily make the repository quite busy/littered with files.
* @wood_value_2021: Not relevant.

**Reflections:** <!--TODO: Update reflections once add Johnson -->

* Outputting hundreds of files - particularly if they are not then used normally in analysis - can easily make repository cluttered/busy

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ✅ | ✅ | <!--TODO--> | ✅ | ✅ |

@@

@hernandez_optimal_2015: Fully met. This ensured consistent results between runs of the script, which was really helpful.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | N/A | 🟡 | ❌ | N/A | <!--TODO--> | ❌ | ✅ |

@@

@hernandez_optimal_2015: Not met.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ❌ | ❌ | <!--TODO--> | 🟡 | ✅ |

@@

@hernandez_optimal_2015: Partially met. Provides a few example `ggplot`s, but these are not all the plots, nor exactly matching article, nor including any of the pre-processing required before the plots, and so could only serve as a starting point (though that was still really handy).

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | N/A | ❌ | N/A | N/A | N/A | N/A |

@@

@lim_staff_2020, @anagnostou_facs-charm_2022, @johnson_cost_2021, @hernandez_optimal_2015, @wood_value_2021: Not applicable (no in-text results).

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | 🟡 | ✅ | <!--TODO--> | ❌ | ❌ |

@@

<!--TODO: Reflect whether any of these should be boxes above-->

**Grid lines**. Include tick marks/grid lines on figures, so it is easier to read across and judge whether a result is above or below a certain Y value.

**Data dictionaries**. @anagnostou_facs-charm_2022: Included data dictionary for input parameters. Although I didn’t need this, this would have been great if I needed to change the input parameters at all.

**Unsupported versions**. @hernandez_optimal_2015: Due to the age of the work:

* Some packages were no longer available on Conda and had to be installed from PyPI
* The version of python was no longer supported which meant:
    * Not supported by Jupyter Lab and Jupyter Notebook (so no `.ipynb` files, or Jupyter Lab on Docker)
    * Not supported by VSCode (so had to use "tricks" to run it, involving using a pre-release version of Python on VSCode)
    * Had to create Docker image from scratch (i.e. couldn't start from e.g. `miniconda3`)

However, this is a slightly unavoidable problem unless you continue to maintain your code (which is ideal but not always feasible in a research environment). Realistically, if reusing this code for a new purpose, you would upgrade it to supported versions.

**Original results files**. @hernandez_optimal_2015: Included some original results files, which was invaluable in identifying some of the parameters in the code that needed to be fixed.

**Classes**. @hernandez_optimal_2015: Structured code into classes, which was nice to work with/amend.

@@

* Include grid lines
* Include data dictionaries
* If feasible, maintain code to avoid dependency on unsupported old versions of packages and languages
* Ideally, include copies of your results, so can (a) compare against, (b) use to run analysis on, and (c) use in troubleshooting
